Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-10-29 robdml.tex
tex

In summary, HM creates mini-batches mixing some unperturbed source triplets and
some adversarial triplets.
%
The $\text{HM}[\mathcal{R}, \mathcal{M}]$ and $\text{HM}[\mathcal{S},
\mathcal{M}]$ achieve such balanced mixtures.
%
Empirically, the hardness range of Semihard strategy is appropriate for
$H_\mathcal{D}$.

\todo{R}

@@

In summary, according to \cref{tab:desth}, HM from random to semihard, or from
softhard to semihard are two choices that can effectively lead to robust
DML model.
%
The subsequent experiments will be based on the two choices.

>>>>

@@

In summary, HM creates mini-batches mixing some unperturbed source triplets and
some adversarial triplets.
%
The $\text{HM}[\mathcal{R}, \mathcal{M}]$ and $\text{HM}[\mathcal{S},
\mathcal{M}]$ achieve such balanced mixtures.
%
Subsequent experiments will be based on the two effective combinations.
%
Empirically, the hardness range of Semihard strategy,
\ie, $[-\gamma,0]$ is appropriate for $H_\mathcal{D}$.
